STA610 Case Study 1 Team 4 Report

### 2021-03-22 final 3.Rmd
changes

---
title: "\vspace{-1.5cm} \textbf{STA610 Case Study 1 Team 4 Report}"
author:
- Cole Juracek (Programmer)
- Lauren Palazzo (Writer)
- Lingyu Zhou (Checker + Coordinator)
- Fan Zhu (Presenter)
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
  pdf_document: default
fontsize: 11pt
geometry: margin=2cm
---

@@

```{r, fig.align='center', fig.height = 2.5}
ggplot(df, aes(x=reorder(USA_region, USA_region, length), y=log_ppm, fill=USA_region)) +
geom_boxplot() +
labs(title="log PPM by region", x="region",y="Log PPM")
```

@@

#### Model Diagnostics
```{r, fig.align='center', warning=FALSE, message=FALSE, error=FALSE}
resqq <- plot_resqq(mod_final)
ranefci <- plot_ranef(mod_final)
grid.arrange(resqq, ranefci, ncol = 2)
```

@@

```{r, fig.align='center', fig.height=8}
plotREsim(REsim(mod_final,n.sims=100),stat='median',sd=TRUE, labs = TRUE)
```
From the result of the random effects, we can see that the random intercept for Tennessee is the highest and it is significantly different from zero. The random intercept for Arizona is the lowest and this intercept is also significant.

## Appendix

@@

# Appendix

@@

### More EDA: slope and intercept distributions for predictors by state
```{r}
# To get a better sense of how state-level groups and slopes are distributed, we created the following intercepts for our coninuous variables:

@@

group_int_list <- NULL 
group_slope_list <- NULL
for(statej in unique(df$state)) {
    m <- lm(data = df[df$state==statej, ], log_ppm ~ dose_per_mg)
    group_int_list <- c(group_int_list, coef(m)[1])
    group_slope_list <- c(group_slope_list, coef(m)[2])
}
par(mfrow=c(1,1))
hist(group_int_list)
hist(group_slope_list)

>>>>

---
title: STA610 Case Study 1 Team 4 Report
author:
- Cole Juracek (Programmer)
- Lauren Palazzo (Writer)
- Lingyu Zhou (Checker + Coordinator)
- Fan Zhu (Presenter)
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document:
    df_print: paged
fontsize: 11pt
geometry: margin=1.5cm
---

@@

```{r, fig.align='center', fig.height = 1.5}
ggplot(df, aes(x=reorder(USA_region, USA_region, length), y=log_ppm, fill=USA_region)) +
geom_boxplot() +
labs(title="log PPM by region", x="region",y="Log PPM")
```

@@

#### Model Diagnostics
```{r error=FALSE, fig.align='center', fig.height=, message=FALSE, warning=FALSE, fig.height=2}
resqq <- plot_resqq(mod_final)
ranefci <- plot_ranef(mod_final)
grid.arrange(resqq, ranefci, ncol = 2)
```

@@

```{r, fig.align='center', fig.height=4}
plotREsim(REsim(mod_final,n.sims=100),stat='median',sd=TRUE, labs = TRUE)
```
From the result of the random effects, we can see that the random intercept for Tennessee is the highest and it is significantly different from zero. The random intercept for Arizona is the lowest and this intercept is also significant.

## Limitation

Our analysis has several limitations. Our filtering of the `log_ppm` variable to non-extreme values must be kept in mind, as we are essentially modeling typical values only, so some unusual price values may not be predicted correctly by our model. Small sample sizes for some states are not ideal, although our hierarchical model structure helps to mitigate this issue. User-input data is naturally messy and should be taken with a grain of salt. Furthermore, our sample is essentially self-selected (people who choose to enter their data into the StreetRx web site) rather than randomly sampled, and this may affect the generalizability of our results.

\newpage
## Appendix

@@

@@

### More EDA: slope and intercept distributions for predictors by state
```{r, fig.width=3}
# To get a better sense of how state-level groups and slopes are distributed, we created the following intercepts for our coninuous variables:

@@

group_int_list <- NULL 
group_slope_list <- NULL
for(statej in unique(df$state)) {
    m <- lm(data = df[df$state==statej, ], log_ppm ~ dose_per_mg)
    group_int_list <- c(group_int_list, coef(m)[1])
    group_slope_list <- c(group_slope_list, coef(m)[2])
}

hist(group_int_list)
hist(group_slope_list)
